### 2015-05-28 writing/SNLI paper/abstract.tex
Implementing CM's suggestions.

\begin{abstract} 
  % Entailment and contradiction are fundamental to natural language
  % meaning and lie at the heart of tasks like summarization, textual
  % entailment, and commonsense reasoning.
  Entailment and contradiction are fundamental to natural language
  meaning and so have emerged (in the form of tasks involving
  reasoning, inference, and summarization) as an important testing
  ground for semantic representations.
  %
  %However, computational modeling of these concepts is currently
  %hampered by the limited nature of existing annotated resources.
  However, progress is currently hampered by the limitations of
  existing annotated resources.
  %
  To address this, we present a new corpus of sentence pairs labeled
  for entailment, contradiction, and semantic independence. At 570K
  pairs, it is orders of magnitude larger than all other resources
  of its type.
  %
  And, in contrast to many such resources, all of the sentences were
  written by humans in a grounded, naturalistic context.
  %
  In this paper, we use this corpus to evaluate a wide variety of
  models for natural language inference, finding that Tree-Structured
  Long Short-Term Memory networks (TreeLSTMs) achieve the best
  performance.
  %
  In addition, to enhance the case for TreeLSTMs, and deepen the
  argument for the centrality of entailment and contradiction in
  semantics, we show that the TreeLSTM's representations, trained on
  our corpus, perform well in a disparate set of additional semantic
  tasks.  
  \todo{Structure more around results (vs. data).}
\end{abstract}

>>>>

\begin{abstract} 
  % Entailment and contradiction are fundamental to natural language
  % meaning and lie at the heart of tasks like summarization, textual
  % entailment, and commonsense reasoning.
  Entailment and contradiction are fundamental to natural language
  meaning and so are an important testing
  ground for semantic representations.
  %
  %However, computational modeling of these concepts is currently
  %hampered by the limited nature of existing annotated resources.
  However, progress is currently hampered by the limitations of
  existing annotated resources for training.
  %
  To address this, we present a new corpus of sentence pairs labeled
  for entailment, contradiction, and semantic independence. At 570K
  pairs, it is orders of magnitude larger than all other resources
  of its type.
  %
  And, in contrast to many such resources, all of the sentences were
  written by humans in a grounded, naturalistic context.
  %
  In this paper, we use this corpus to evaluate a wide variety of
  models for natural language inference, finding that Tree-Structured
  Long Short-Term Memory networks (TreeLSTMs) achieve the best
  performance.
  %
  In addition, to enhance the case for TreeLSTMs, and deepen the
  argument for the centrality of entailment and contradiction in
  semantics, we show that the TreeLSTM's representations, trained on
  our corpus, perform well in a disparate set of additional semantic
  tasks.  
\end{abstract}

### 2015-05-28 writing/SNLI paper/corpus.tex
Implementing CM's suggestions.

To date, the primary sources of annotated NLI corpora have been the
Recognizing Textual Entailment (RTE)
tasks.\footnote{\url{http://aclweb.org/aclwiki/index.php?title=Textual_Entailment_Resource_Pool}}
These are generally high-quality, hand-labeled data sets, and they
have stimulated innovative logical and statistical models of natural
language reasoning, but their small size (a few hundred examples each)
limits their utility as a testbed for learned distributed representations. 
The data for the SemEval 2014 task called Sentences Involving Compositional Knowledge (SICK) is a
step up in terms of size, but only to 4,500 training examples, and its
partly automatic construction introduced some spurious patterns into
the data (\citealt{marelli2014semeval}, $\S$6). Finally, the
Denotation Graph entailment set \cite{hodoshimage} contains millions of
examples of entailments between sentences and artificially constructed
short phrases, but it was labeled using fully automatic methods, and is
noisy enough that it is probably suitable only as a source of
supplementary training data. The Paraphase Database of \cite{ganitkevitch2013ppdb}
addresses these issues of size and quality, but only for the limited
fragment of the NLI problem that is captured by paraphase.

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label \cite{marelli2014sick}. For
instance, the sentence pair \word{A boat sank in the Pacific
  ocean} and \word{A boat sank in the ocean} could reasonably be labeled in
numerous ways depending on how the objects and events are grounded. If
the two boats are assumed to be different, then the sentences are semantically
independent. If the boats and the oceans are assumed to be the same,
then the first sentence entails the second (in the relevant
commonsense way). If the boats are assumed to be the same and 
\word{the ocean} in the second sentence is interpreted with a specific referent 
that is not the Pacific, then the two events are (commonsense) contradictory. This
kind of indeterminacy can be resolved only once the questions of
coreference are resolved.

\noindent\todo{Introduce name of corpus.}

@@

For each pair that we validated, we chose a gold label. If any one of
the three labels was chosen by at least three of the five annotators,
that label is the gold label. If there was no such consensus, which
occurred in about 0.2\% of cases, we chose the label `-'. While these
unlabeled examples are included in the corpus distribution, they are
unlikely to be helpful for the standard NLI classification task, and
we do not include them when training and evaluating the models
discussed in later sections. The results of this validation process
are summarized in Table \ref{validation-stats}. 
Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing. The Fleiss $\kappa$ scores 
(computed over every example with a full five annotations)
are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rates of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

\noindent\todo{More on *why* `-' isn't a valid test label}

@@

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{6cm}p{0.75cm}p{1.4cm}p{6cm}}
  \toprule
A man inspects the uniform of a figure in some East Asian country. & \b{contr.}& \t{$\{$c c c c c$\}$} & The man is sleeping\\
\rule{0pt}{3ex}An older and younger man smiling. & \b{neut.}& \t{$\{$n n e n n$\}$} & Two men are smiling and laughing at the cats playing on the floor.\\
\rule{0pt}{3ex}A black race car starts up in front of a crowd of people. & \b{contr.}& \t{$\{$c c c c c$\}$} & A man is driving down a lonely road.\\
\rule{0pt}{3ex}A soccer game with multiple males playing. & \b{ent.}& \t{$\{$e e e e e$\}$} & Some men are playing a sport.\\
\rule{0pt}{3ex}A smiling costumed woman is holding an umbrella. & \b{neut.}& \t{$\{$n n e c n$\}$} & A happy woman in a fairy costume holds an umbrella.\\
    \bottomrule
% From 1.0rc3
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from the SNLI development set, shown with the gold labels and the full set of annotator labels (abbreviated). Unlike in many existing NLI corpora, the premise and hypothesis sentences in SNLI are often too dissimilar in structure to support approaches to NLI that rely on building sentence-to-sentence alignments.}
\end{table*}

Table~\ref{snli-examples} shows a set of randomly chosen validated examples from the development set with their labels. Qualitatively, we find the data that we collected to draw fairly extensively on commonsense knowledge, suggesting that superficial word alignment models are unlikely to be able to succeed at classification. We find the sentences that we collected be largely fluent, correctly spelled English, with a mix of full sentences and caption-style noun phrase fragments. Punctuation and capitalization are often omitted.

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
\multicolumn{2}{l}{\textbf{Data set sizes:}}\\
Training pairs &  550,152\\
Development pairs &  10,000\\
Test pairs & 10,000\\
\midrule
\multicolumn{2}{l}{\textbf{Sentence length:}}\\
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
\multicolumn{2}{l}{\textbf{Parser output:}}\\
Premise `S'-rooted parses & 74.0\%\\
Hypothesis `S'-rooted parses & 88.9\%\\
Unique word tokens (ignoring case) & ...\\
    \bottomrule
  \end{tabular}
% From 1.0rc3
\todo{Unique word count.}
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report some statistics for both.} 
\end{table}

@@

The distributed corpus includes parses for every sentence produced by the Stanford PCFG Parser \cite{klein2003accurate} (trained on the standard training set as well as on the Brown Corpus; \citealt{francis1979brown}), both in the standard PTB format and in the binarized unlabeled format used by tree-structured neural network models, as in \S\ref{sentence-embedding}.

>>>>

To date, the primary sources of annotated NLI corpora have been the
Recognizing Textual Entailment (RTE)
tasks.\footnote{\url{http://aclweb.org/aclwiki/index.php?title=Textual_Entailment_Resource_Pool}}
These are generally high-quality, hand-labeled data sets, and they
have stimulated innovative logical and statistical models of natural
language reasoning, but their small size (fewer than a thousand examples each)
limits their utility as a testbed for learned distributed representations. 
The data for the SemEval 2014 task called Sentences Involving Compositional Knowledge (SICK) is a
step up in terms of size, but only to 4,500 training examples, and its
partly automatic construction introduced some spurious patterns into
the data (\citealt{marelli2014semeval}, $\S$6). Finally, the
Denotation Graph entailment set \cite{hodoshimage} contains millions of
examples of entailments between sentences and artificially constructed
short phrases, but it was labeled using fully automatic methods, and is
noisy enough that it is probably suitable only as a source of
supplementary training data. The Paraphase Database of \cite{ganitkevitch2013ppdb}
addresses these issues of size and quality, but only for the limited
fragment of the NLI problem that is captured by paraphase.

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label \cite{marelli2014sick}. For
instance, the sentence pair \word{A boat sank in the Pacific
  ocean} and \word{A boat sank in the ocean} could reasonably be labeled in
numerous ways depending on how the objects and events are grounded. If
the two boats are assumed to be different, then the sentences are semantically
independent. If the boats and the oceans are assumed to be the same,
then the first sentence entails the second (in the relevant
commonsense way). If the boats are assumed to be the same and 
\word{the ocean} in the second sentence is interpreted with a specific referent 
that is not the Pacific, then the two events are (commonsense) contradictory. This
kind of indeterminacy can be resolved only once the questions of
coreference are resolved.
\todo{Cite Marneffe `08 \S4.3 for coref issue.}

@@

For each pair that we validated, we chose a gold label. If any one of
the three labels was chosen by at least three of the five annotators,
that label is the gold label. If there was no such consensus, which
occurred in about 0.2\% of cases, we chose the label `-'. While rare these
unlabeled examples are included in the corpus distribution, they are
unlikely to be helpful for the standard NLI classification task, and
we do not include them when training and evaluating the models
discussed in later sections. The results of this validation process
are summarized in Table \ref{validation-stats}. 
Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing. The Fleiss $\kappa$ scores 
(computed over every example with a full five annotations)
are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rates of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{6cm}p{0.75cm}p{1.4cm}p{6cm}}
  \toprule
A man inspects the uniform of a figure in some East Asian country. & \b{contr.}& \t{$\{$c c c c c$\}$} & The man is sleeping\\
\rule{0pt}{3ex}An older and younger man smiling. & \b{neut.}& \t{$\{$n n e n n$\}$} & Two men are smiling and laughing at the cats playing on the floor.\\
\rule{0pt}{3ex}A black race car starts up in front of a crowd of people. & \b{contr.}& \t{$\{$c c c c c$\}$} & A man is driving down a lonely road.\\
\rule{0pt}{3ex}A soccer game with multiple males playing. & \b{ent.}& \t{$\{$e e e e e$\}$} & Some men are playing a sport.\\
\rule{0pt}{3ex}A smiling costumed woman is holding an umbrella. & \b{neut.}& \t{$\{$n n e c n$\}$} & A happy woman in a fairy costume holds an umbrella.\\
    \bottomrule
% From 1.0rc3
  \end{tabular}
  \caption{\label{snli-examples}Randomly chosen examples from our development set, shown with the gold labels and the full set of annotator labels (abbreviated). Unlike in many existing NLI corpora, the premise and hypothesis sentences in our corpus are often too dissimilar in structure to support approaches to NLI that rely on building sentence-to-sentence alignments.}
\end{table*}

Table~\ref{snli-examples} shows a set of randomly chosen validated examples from the development set with their labels. Qualitatively, we find the data that we collected to draw fairly extensively on commonsense knowledge, suggesting that superficial word alignment models are unlikely to be able to succeed at classification. We find the sentences that we collected to be largely fluent, correctly spelled English, with a mix of full sentences and caption-style noun phrase fragments. Punctuation and capitalization are often omitted.

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
\multicolumn{2}{l}{\textbf{Data set sizes:}}\\
Training pairs &  550,152\\
Development pairs &  10,000\\
Test pairs & 10,000\\
\midrule
\multicolumn{2}{l}{\textbf{Sentence length:}}\\
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
\multicolumn{2}{l}{\textbf{Parser output:}}\\
Premise `S'-rooted parses & 74.0\%\\
Hypothesis `S'-rooted parses & 88.9\%\\
Distinct words (ignoring case) & 37,026\\
    \bottomrule
  \end{tabular}
% From 1.0rc3
\todo{Unique word count.}
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report some statistics for both.} 
\end{table}

@@

The distributed corpus includes parses for every sentence produced by the Stanford PCFG Parser \cite{klein2003accurate}, trained on the standard training set as well as on the Brown Corpus \cite{francis1979brown}, which we found to improve the parse quality of the descriptive sentences and noun phrases found in the descriptions). Parses are available in both the standard PTB format and in the binarized unlabeled format used by tree-structured neural network models, as in \S\ref{sentence-embedding}.

### 2015-05-28 writing/SNLI paper/entailment_eval.tex
Implementing CM's suggestions.

\section{SNLI as a platform for NLI research}

The most immediate application for the SNLI corpus is in developing models for the task of NLI. In particular, since SNLI is dramatically larger than any existing corpus of comparable quality, we expect it to make possible the use of parameter-rich models like neural networks for this task. In this section, we explore the performance of a range of standard and novel models trained on the corpus.

\subsection{Standard entailment models}
We evaluate a number of strong baselines on the SNLI corpus.
The first class of baselines use models from the Excitement Open
  Platform (EOP,
  \citealt{pado2014design,magnini2014excitement})
  -- an open source platform for RTE research.
%  which
%  is distributed alongside a number of RTE pipelines.
We additionally evaluate against a strong classifier-based baseline based on
  both  unlexicalized and lexicalized features.

@@

%% methodology
%We convert the 3-way classification task in SNLI into the RTE setting
%  by labeling both the \unknown\ and \contradiction\
%  labels as negative entailment, and treating the \entailment\ label as
%  the positive entailment.
%This creates a biased dataset of 66\% negative examples.
% we report the best results from each class
We run the top performing edit-distance based algorithm and the top
  performing classifier-based algorithm on the SNLI test set, as
  determined by performance on the development set.
Note that these models were run using the default configuration
  with minimal tuning.
The results should therefore be taken as a strong baseline for
  RTE-style approaches to the problem, rather than necessarily
  representing the state-of-the-art system's performance on the
  task.
%We run each of the 9 algorithms distributed with EOP on the 2-class
%  SNLI dataset, and report results for the best edit distance 
%  configuration and the best classifier based configuration, as
%  determined by performance on the development set.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{SNLI}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{Final numbers}
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

%
% Lexicalized Classifier
%
\paragraph{Lexicalized Classifier}
Unlike the RTE datasets, SNLI's size allows approaches which make use of
  rich lexicalized features.
We implement such a lexicalized classifier as a strong baseline 
  for the task.
Our classifier implements 6 features:
\begin{enumerate}
\setlength\itemsep{-0.25em}
  \item the BLEU score of the \hypothesis\ with respect
  to the \premise, using an n-gram length between 1 and 4.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceM}c}
\hline
\textbf{System} & \b{Dev} & \multicolumn{4}{c}{\b{Test}} \\
 & \t{Acc.} & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{79.4} & \t{82.3} & \t{80.9} & \t{78.2} \\
\t{Unigrams Only}          & \t{??.?} & \t{71.1} & \t{77.7} & \t{74.3} & \t{71.6} \\
\t{Unlexicalized}          & \t{??.?} & \t{56.0} & \t{64.4} & \t{59.9} & \t{50.39} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the SNLI dataset, including precision/recall for the
  \textit{entailed} class on the test set.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
\todo{Final numbers}
}
\end{table}
%
% END BOW RESULTS TABLE
%

@@

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the RTE baselines -- this is in some sense unsurprising:
  the RTE systems have been tuned on relatively small corpora
  ($\sim$1600 examples), whereas a classifier trained on SNLI can make use of
  over two orders of magnitude more data.

@@

SNLI is uniquely suitable for training neural network models that produce vector representations of sentence meaning. In this section, we compare the performance of six such models on SNLI. 
In order to best evaluate the strengths of these six models at producing informative representations, we use sentence embedding as an intermediate step in the NLI classification task: each model most produce vector representation of each of the two sentences without using any context from the other sentence, and the two resulting vectors are then passed to a neural network classifier which predicts the label for the pair. This choice allows us to focus on evaluating the ability of existing models to produce representations that fully capture sentence meaning, at the possible cost of excluding from consideration neural models for NLI that directly compare the two inputs at the word or phrase level.

@@

The word embeddings for all of the models are initialized the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{67?} & \t{69?} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers/dims}
}
\end{table}

>>>>

\section{Our data as a platform for NLI research}

The most immediate application for our corpus is in developing models for the task of NLI. In particular, since it is dramatically larger than any existing corpus of comparable quality, we expect it to be suitable for training  parameter-rich models like neural networks for this task. In this section, we explore the performance of a range of standard and novel models trained on the corpus.

\subsection{Standard entailment models}
We evaluate a number of strong baselines on our corpus.
The first class of baselines use models from the Excitement Open
  Platform (EOP,
  \citealt{pado2014design,magnini2014excitement})
  -- an open source platform for RTE research.
%  which
%  is distributed alongside a number of RTE pipelines.
We additionally evaluate against a strong classifier-based baseline based on
  both  unlexicalized and lexicalized features.

@@

%% methodology
%We convert the 3-way classification task in SNLI into the RTE setting
%  by labeling both the \unknown\ and \contradiction\
%  labels as negative entailment, and treating the \entailment\ label as
%  the positive entailment.
%This creates a biased dataset of 66\% negative examples.
% we report the best results from each class
We run the top performing edit-distance based algorithm and the top
  performing classifier-based algorithm on our test set, as
  determined by performance on the development set.
Note that these models were run using the default configuration
  with minimal tuning.
The results should therefore be taken as a strong baseline for
  RTE-style approaches to the problem, rather than necessarily
  representing the state-of-the-art system's performance on the
  task.
%We run each of the 9 algorithms distributed with EOP on the 2-class
%  SNLI dataset, and report results for the best edit distance 
%  configuration and the best classifier based configuration, as
%  determined by performance on the development set.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{Our corpus}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{Final numbers}
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

%
% Lexicalized Classifier
%
\paragraph{Lexicalized Classifier}
Unlike the RTE datasets, our corpus's size allows approaches which make use of
  rich lexicalized features.
We implement such a lexicalized classifier as a strong baseline 
  for the task.
Our classifier implements 6 features:
\begin{enumerate}
\setlength\itemsep{-0.25em}
  \item the BLEU score of the \hypothesis\ with respect
  to the \premise, using an n-gram length between 1 and 4.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceM}c}
\hline
\textbf{System} & \b{Dev} & \multicolumn{4}{c}{\b{Test}} \\
 & \t{Acc.} & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{79.4} & \t{82.3} & \t{80.9} & \t{78.2} \\
\t{Unigrams Only}          & \t{??.?} & \t{71.1} & \t{77.7} & \t{74.3} & \t{71.6} \\
\t{Unlexicalized}          & \t{??.?} & \t{56.0} & \t{64.4} & \t{59.9} & \t{50.39} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the our dataset, including precision/recall for the
  \textit{entailed} class on the test set.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
\todo{Final numbers}
}
\end{table}
%
% END BOW RESULTS TABLE
%

@@

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the RTE baselines -- this is in some sense unsurprising:
  the RTE systems have been tuned on relatively small corpora
  ($\sim$1600 examples), whereas a classifier trained on our corpus can make use of
  over two orders of magnitude more data.
  \todo{Use curve to justify large size of corpus.}

@@

Our corpus is uniquely suitable for training neural network models that produce vector representations of sentence meaning. In this section, we compare the performance of six such models on the corpus. 
In order to best evaluate the strengths of these six models at producing informative representations, we use sentence embedding as an intermediate step in the NLI classification task: each model must produce a vector representation of each of the two sentences without using any context from the other sentence, and the two resulting vectors are then passed to a neural network classifier which predicts the label for the pair. This choice allows us to focus on evaluating the ability of existing models to produce representations that fully capture sentence meaning, at the possible cost of excluding from consideration neural models for NLI that directly compare the two inputs at the word or phrase level.

@@

The word embeddings for all of the models are initialized with the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{67?} & \t{69?} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the our training and test sets for each model.
\todo{Replace with final numbers/dims}
}
\end{table}
